### 2021-12-15 README.Rmd
disclamer documentation on contact matrices structure

>>>>

## Disclaimer

The contact matrices created using the package are transposed compared to the contact matrices discussed by [Prem](https://journals.plos.org/ploscompbiol/article?id=10.1371/journal.pcbi.1005697#pcbi.1005697.ref023) and [Mossong](https://journals.plos.org/plosmedicine/article?id=10.1371/journal.pmed.0050074).
